{\color {red}better title eventually}

### 2015-05-12 cs261n-paper/paper.tex
List of UX Sprint tasks.
I got it from tasks.html from
https://repo.eecs.berkeley.edu/git-anon/users/fifield/tor-ux.git.

\subsection{Experiment Overview}
{\color {red} Talk about how the experiment was for an average user. We start
with the cognitive walkthrough, then have them do one on a dummy
and calibration task, we give feedback on the walkthrough, and then 
give them the freedom to complete the web tasks.

GET THE LIST OF TASKS WE MADE THEM DO.}

>>>>

\subsection{Experiment Overview}
{\color {red} Talk about how the experiment was for an average user. We start
with the cognitive walkthrough, then have them do one on a dummy
and calibration task, we give feedback on the walkthrough, and then 
give them the freedom to complete the web tasks.}

After the calibration task, we asked participants to complete
the following Tor Browser--related tasks:
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item Download Tor (the web browser)
\item Install Tor
\item Check that Tor is working
\item Do a web search for ``onions''
\item Find a YouTube video for ``Ode to Joy''
\item Use ``New Identity'' under the onion menu
\item Explain your best understanding of all the items in the toolbar
\end{enumerate}
We originally had another step after Step~1, ``Configure Tor.''
We removed it after the first two participants
when it became clear that the wording was confusing.
The two main buttons in the configuration wizard are labeled
``Connect'' and ``Configure''; we did not intend for users
to have to go through the longer ``Configure'' path,
but they assumed they had to because of the presence
of the word ``Configure'' in the list of tasks.
